Ensemble Stability of Biological Networks

### 2014-09-25 paper.tex
remove excess information

In order to evaluate these integrals, one needs to describe the stable region.
The theory of how to do so in terms of conditions on the coefficients of the
characteristic polynomials was developed by various mathematicians during the
second half of the nineteenth century and is summarized in chapter XV of
\cite{Gantmacher1959}.  We now summarize some of these results which are
relevant to our calculations.

\todo{Finish writing these criteria with reference to Gantmacher}
Define the characteristic polynomial as $\chi(M)(z) = \det(zI - M)$.
Denote the coefficients of $\chi(M)$ as $s_j$ and its roots as $r_j$,
writing $p(x) = x^n + \sum_{k=1}^n s_k x^{n-k} = \prod_{k=1}^n (x-r_k)$.
Then, since the roots of $\chi$ are the eigenvalues of $M$, asking that
$M$ be stable is equivalent to asking that the roots of $\chi$ all have
negative real part.  Hence, let us call a polynomial stable if all its
roots have negative real part.  We will formulate conditions for this to
happen in terms of the coefficients of $\chi$ \cite{Gantmacher1959}.

\begin{lemma}
If $M$ is stable, then $s_i > 0$ for all $i$ between $1$ and $n$.
\end{lemma}
\begin{lemma}
If a point lies on the boundary of the set of stable polynomials, then
either $s_n = 0$ and $\Delta = 0$.
\end{lemma}
\begin{lemma}
If $n < 6$, then a polynomial $p$ is stable if and only
if $\Delta > 0$ and $s_1 > 0$ for all $i$.
\end{lemma}

>>>>

In order to evaluate these integrals, one needs to describe the stable region.
This can be done in terms of conditions on the coefficients of the
characteristic polynomials associated to the systems described by matrices $A$ above \cite{Gantmacher1959}.
